\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

While our findings indicate many areas for further improvement of \gls{llm}-based systems, it is also important to realize that clearly defined metrics have been the key to the progress of many fields of \gls{ml}, such as computer vision.
Although current systems might be far from reasoning like a chemist, our \chembench framework will be a stepping stone for developing systems that might come closer to this goal.

>>>>

While our findings indicate many areas for further improvement of \gls{llm}-based systems, such as for agents (more discussion in \cref{sec:react-environment}), it is also important to realize that clearly defined metrics have been the key to the progress of many fields of \gls{ml}, such as computer vision.
Although current systems might be far from reasoning like a chemist, our \chembench framework will be a stepping stone for developing systems that might come closer to this goal.
